Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-04-28 paper.tex
Assigning TODOS

%***TODO***: talking about the machines used
% Done - %---  Sam
% Please don't use real text for TODOs- JJ
%Experiments have been conducted on an Intel(R) Core(TM) i5-4430 CPU at 3.00GHz 
%(4 cores) and 16 GB RAM, running Ubuntu Linux 14.04.1 LTS and Java JRE\_1.7.0\_72.

@@

As far as the different methods is concerned, M5P model obtained good results, 
both in time and error, and as stated before, this method can learn and tackle 
tasks with high dimensionality and it generates reproducible and comprehensible 
representations that provide information on the decision process and does not 
require human intervention either for the operation or for interpretation. 
Thus, it is very suitable in order to be incorporated in a publishing company 
processes.

@@

% Antonio - TODO: explain the aim of FS in these experiments.
% Sam : Done

@@

%***TODO***: describe the parameters of SOM (size, neighbourhood shape, etc) and obtained quantisation and topographical errors.

% The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data. The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.

@@

%***TODO***: Justify the selected features by SOM (why have we chosen them?).

@@

%***TO DO***: comment the results

@@

***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.

@@

***TO DO:*** better explain this

We have considered the best seller editorial as a good example case to show.

@@

***TO DO***: better justify this\\

@@

@@

***TO DO***: rewrite these conclusions with the new experiments, examples and results\\

>>>>

@@

As far as the different methods are concerned, M5P model obtained good results, 
both in time and error, and as stated before, this method can learn and tackle 
tasks with high dimensionality and it generates reproducible and comprehensible 
representations that provide information on the decision process and does not 
require human intervention either for the operation or for interpretation. 
Thus, it is very suitable in order to be incorporated in a publishing company 
processes.

@@

@@

The SOM algorithm is applied with a large map size of $26 \times 16$  in order to represent the data. The best SOM training results are obtained with a final quantisation error of 0.691 and topographic error of 0.046.

@@

%***TODO***: Justify the selected features by SOM (why have we chosen them?).
% Sam will do it

@@

%***TO DO***: comment the results
% Sam will do it - JJ

@@

%***TO DO***: explain we have chosen the best Feature selection method (ReliefAttributeEval???). The rest of tables have been moved to an appendix.
%Sam will do it - JJ

@@

%***TO DO:*** better explain this
% Sam will do it

We have considered the publisher that sells the most as a good example case to show.

@@

%***TO DO***: better justify this\\

@@

%***TO DO***: comments on the figure\\

@@

%***TO DO***: rewrite these conclusions with the new experiments, examples and results\\
